\documentclass[11pt]{handout}
\usepackage{moreverb}
\usepackage{tabularx}
\usepackage{epsf}
\usepackage{epic}
\usepackage{eepic}
\usepackage{epsfig}
\usepackage{epsf}
\usepackage{fancyheadings}
\usepackage{fancybox}

\renewcommand{\coursetitle}{ECE 320}
\renewcommand{\handouttitle}{Carrier Recovery}
\renewcommand{\handoutauthor}{Michael Kramer}
\renewcommand{\semestertitle}{Spring 2000}

\newcommand{\blt}{\mbox{$\bullet$ }}

\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}

\setlength{\parindent}{5mm}
\begin{document}

\setlength{\baselineskip}{0.5cm}
\setlength{\parskip}{0.5cm}

\makeboxtitle
\vspace{0.3cm}

\section{Introduction:}

This handout is designed to provide you with a brief
description on the carrier recovery sub-system of a digital receiver 
and addresses some of the details associated with its 
implementation/simulation in \matlab and on the DSP.
The sub-system covered is specifically tailored to a
non-modulated carrier.  In the final PLL implementation used for
your digital receiver you will have to make modifications
to the specific details mentioned.

\input{carrier_recovery_theory_tutorial}

\section{Matlab Simulation:}

\input{carrier_recovery_matlab_exercise}

\section{DSP Implementation:}

As you begin to implement your PLL on the DSP it is highly
recommended that you implement and 
test your NCO block first before completing the rest
of the phase-locked loop.

\input{carrier_recovery_processor_exercise}

\section{Extensions}

As your final project will require some modification to the discussed
non-modulated carrier recovery, you will want to refer to the listed 
references, \cite{Proakis1, Blahut1},
and consider some of the following questions regarding such 
modifications:

\blt How does the addition of noise affect the described carrier recovery 
method?

\blt What should the phase-detector look like for a BPSK modulated carrier?

\vspace*{-.1in}
\hspace{.1in} (Hint: you now need to consider both the in-phase and 
quadrature channels.)

\blt How does $\alpha$ affect the bandwidth of the loop-filter?

\blt How does the loop-gain, $K$, and the bandwidth of the loop-filter
affect the PLL's ability to lock onto a carrier frequency mismatch?

\bibliographystyle{ieeetr}
\bibliography{../../ece320}


\end{document}
\bye
