\documentclass[11pt]{handout}
\usepackage{moreverb}
\usepackage{epsf}
\usepackage{epic}
\usepackage{eepic}

\renewcommand{\coursetitle}{ECE 320}
\renewcommand{\handouttitle}{Audio Effects: Delay}
\renewcommand{\handoutauthor}{Daniel Sachs}
\renewcommand{\semestertitle}{Fall 1999}

\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}

\setlength{\parindent}{5mm}
\begin{document}

\setlength{\baselineskip}{0.5cm}
\setlength{\parskip}{0.5cm}

\makeboxtitle
\vspace{0.3cm}

\section{Introduction}

In this project lab, we will introduce the DSP memory
map and describe how to store a large amount of data on the EVM.
We will then use this to implement a long audio delay and an
audio echo.

The TI DSP evaluation boards we are using in this class have a large
amount of memory - 32k words internal to the DSP itself and
another 256k words on the EVM board. During the lab portion 
of this course, we used only
the board-mounted memory, and didn't really consider how much
we were using or the differences between internal and external RAM.
However, in order to generate large delays - which are often required in 
audio processing - we need to use a significant portion of the
memory on the DSP board. And in order to achieve the DSP's peak 
performance, we need to use the on-chip memory to reduce the time
the DSP spends waiting for data.

In this lab, you will explore the memory map of the DSP board,
and learn how to access all of the memory on the board. You will
then apply this knowledge to build a very long delay line. Finally,
you will modify the delay line to delay the input by an arbitrary
number of points, then feed back the delayed signal into the input.
This will result in a simple echo effect.

\section{EVM Memory Maps}

\input{evm_memory_maps_54x_tutorial}

To make this lab simpler, you will
may leave the overlay mode off and disable internal program memory for
this lab. In Lab II, we will address switching the overlay mode on
and off "on the fly" to achieve better performance.

Note that the \verb+thru.asm+ file you have been given disables the
overlay mode, so you won't need to worry about switching out of it
for this lab.

\section{Accessing Extended Program RAM}

\input{accessing_extended_program_ram_54x_tutorial.tex}

\section{Delay and Echo Implementation}

\input{external_memory_processor_exercise}

\end{document} 
